Circumcision Paper Text

### 2024-04-15 paper/paper_cals.Rmd
successful knit

The largest increase from 2006 to 2020 in MC coverage for 10-29 year olds amongst VMMC priority countries was in 
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(iso3) %>% to_cntry_name()`, 
from 
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean_2006) %>% to_percentage()`
(
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(lower_2006) %>% to_percentage()`
-
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(upper_2006) %>% to_percentage()`
) in 2006 to 
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean_2020) %>% to_percentage()`
(
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean_2020) %>% to_percentage()`
-
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean_2020) %>% to_percentage()`
) in 2020, a 
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean_diff) %>% to_percentage()`
(
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(lower_diff) %>% to_percentage()`
-
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(upper_diff) %>% to_percentage()`
) increase. 
In contrast, the lowest increase in MC coverage in these countries was in 
from 
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean_2006) %>% to_percentage()`
(
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(lower_2006) %>% to_percentage()`
-
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(upper_2006) %>% to_percentage()`
) in 2006 to 
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean_2020) %>% to_percentage()`
(
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean_2020) %>% to_percentage()`
-
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean_2020) %>% to_percentage()`
) in 2020, a 
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean_diff) %>% to_percentage()`
(
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(lower_diff) %>% to_percentage()`
-
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(upper_diff) %>% to_percentage()`
) increase.

>>>>

The largest increase from 2006 to 2020 in MC coverage for 10-29 year olds amongst VMMC priority countries was in 
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(iso3) %>% to_cntry_name()`, 
from 
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean_2006) %>% to_percentage()`
(
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(lower_2006) %>% to_percentage()`
-
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(upper_2006) %>% to_percentage()`
) in 2006 to 
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean_2020) %>% to_percentage()`
(
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean_2020) %>% to_percentage()`
-
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean_2020) %>% to_percentage()`
) in 2020, a 
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(diff_mean) %>% to_percentage()`
(
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(diff_lower) %>% to_percentage()`
-
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(diff_upper) %>% to_percentage()`
) increase. 
In contrast, the lowest increase in MC coverage in these countries was in 
from 
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean_2006) %>% to_percentage()`
(
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(lower_2006) %>% to_percentage()`
-
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(upper_2006) %>% to_percentage()`
) in 2006 to 
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean_2020) %>% to_percentage()`
(
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean_2020) %>% to_percentage()`
-
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean_2020) %>% to_percentage()`
) in 2020, a 
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(diff_mean) %>% to_percentage()`
(
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(diff_lower) %>% to_percentage()`
-
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(diff_upper) %>% to_percentage()`
) increase.
